Still Missing a Cool Title

### 2006-05-31 talk/dls2006/paper.tex
add a missing "section"

In the example of the \texttt{malloc} operation, replaced by a call to
GC code, this GC code can invoke a complete collection of dead
objects, and can thus be arbitrarily complicated.  Still, our GC code
is entirely written in plain Python, and it manipulates "objects" that
are still at a lower level: pointer and address objects.  Even with
the restriction of having to use pointer-like and address-like
objects, Python remains more expressive than, say, C to write a GC
(Jikes RVM's GC work \cite{JikesGC} was the inspiration to try to
express GCs in Python, see \ref{relatedwork}).

>>>>

In the example of the \texttt{malloc} operation, replaced by a call to
GC code, this GC code can invoke a complete collection of dead
objects, and can thus be arbitrarily complicated.  Still, our GC code
is entirely written in plain Python, and it manipulates "objects" that
are still at a lower level: pointer and address objects.  Even with
the restriction of having to use pointer-like and address-like
objects, Python remains more expressive than, say, C to write a GC
(Jikes RVM's GC work \cite{JikesGC} was the inspiration to try to
express GCs in Python, see section \ref{relatedwork}).
